Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-12-07 script/manuscript_MEE.Rmd
appenddix formats added but need go back and iron out deposition and which slides were made to pollen vouchers in the end

```{r APPENDIX NUMBER LOCI WITH READS USED IN MATCHING, echo = F}
knitr::include_graphics('../graphics/plots/Percent_loci_matched_by_sample.png')
```

@@

```{r APPENDIX NUMBER RMBL Pollen Key 1, echo = F}
knitr::include_graphics('../graphics/assorted/RMBL_pollen_key-1.pdf')
```

@@

```{r APPENDIX NUMBER RMBL Pollen Key 2, echo = F}
knitr::include_graphics('../graphics/assorted/RMBL_pollen_key-2.pdf')
```

@@

@@

```{r APPENDIX MORPHOTYPE RICHNESS AND ABUNDANCE, echo= F}
knitr::include_graphics('../graphics/plots/species_richness_rarefaction.png')
```

@@

```{r, echo = F, out.width = '25%'}
knitr::include_graphics('../graphics/plots/SppAbundance.png')
```

@@

```{r Voucher Reference Specimen tables 1, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-1.pdf')
```

@@

```{r Voucher Reference Specimen tables 2, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-2.pdf')
```

@@

>>>>

Appendix XX - Reads Per Loci

```{r READS PER LOCI, echo = F}
knitr::include_graphics('../graphics/plots/Percent_loci_matched_by_sample.png')
```

@@

Appendix XX - Pollen Key

```{r Pollen Key 1, echo = F}
knitr::include_graphics('../graphics/assorted/RMBL_pollen_key-1.pdf')
```

@@

```{r Pollen Key 2, echo = F}
knitr::include_graphics('../graphics/assorted/RMBL_pollen_key-2.pdf')
```

@@

Appendix XX - Species Distribution Models Predictors

@@

APPENDIX XX - Pollen Morphotype Richness Rarefaction Curves

```{r Morphotype Richness, echo= F}
knitr::include_graphics('../graphics/plots/species_richness_rarefaction.png')
```

@@

Appendix XX - Pollen Morphotype Abundance Rarefaction Curves

```{r Morphotype Abundance, echo = F, out.width = '25%'}
knitr::include_graphics('../graphics/plots/SppAbundance.png')
```

@@

Appendix XX - Molecular Reference Specimen Table

```{r Voucher Reference Specimen table 1, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-1.pdf')
```

@@

```{r Voucher Reference Specimen table 2, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-2.pdf')
```

@@

Appendix XX - All Species in the Sequence Databases

```{r Seq DB 1, echo = F}
knitr::include_graphics('../graphics/assorted/kraken_db_spp_table-1.pdf')
```

```{r Seq DB 2, echo = F}
knitr::include_graphics('../graphics/assorted/kraken_db_spp_table-2.pdf')
```

```{r Seq DB 3, echo = F}
knitr::include_graphics('../graphics/assorted/kraken_db_spp_table-3.pdf')
```

```{r Seq DB 4, echo = F}
knitr::include_graphics('../graphics/assorted/kraken_db_spp_table-4.pdf')
```

Appendix XX - All Pollen Reference Slides Used to Establish Morphotypes

```{r Pollen Reference Slides 1, echo = F}
knitr::include_graphics('../graphics/assorted/pollen_slide_table_reduced-1.pdf')
```

```{r Pollen Reference Slides 2, echo = F}
knitr::include_graphics('../graphics/assorted/pollen_slide_table_reduced-2.pdf')
```

```{r Pollen Reference Slides 3, echo = F}
knitr::include_graphics('../graphics/assorted/pollen_slide_table_reduced-3.pdf')
```
